Ice sheet mass flows

### 2025-08-21 sankey.tex
No FRONTRET or FRONTADV in Sankey (not needed when 0)

    \sankeyset{
      def data/.code args={#1/#2/#3}{% node name/label/values
        \LabSet{#1}{#2}
        \QSet{#1}{#3}
        \typeout{#1: \Q{#1} Gt (\Lab{#1})}
      },
      def data/.list={
        %% INSERT_CSV_HERE
        %% COMPUTED
        {vSMBin/SMB Inputs/\Q{vSF}+\Q{vRF}+\Q{vCD}+\Q{vDP}},
        {vINPUT/Inputs/\Q{vSMBin}+\Q{vFRONTADV}+\Q{vSHELFFREEZE}},
        {vSMBout/SMB Outputs/\Q{vSU}+\Q{vRU}+\Q{vEV}},
        {vDYN/Dynamics/\Q{vCALV}+\Q{vFRONTMELT}+\Q{vSHELFMELT}+\Q{vFRONTRET}+\Q{vGZRET}+\Q{vBMB}},
        {vOUTPUT/Outputs/\Q{vSMBout}+\Q{vDYN}},
        {vSMB/SMB/\Q{vSMBin}-\Q{vSMBout}},
        {vML/Drawdown; Retreat/\Q{vOUTPUT}-\Q{vINPUT}},
        {vMG/Build-up; Expansion/\Q{vINPUT}-\Q{vOUTPUT}}
      },
    }

@@

    \ifthenelse{\Q{vML} > \Q{vMG}} { % mass loss
      \sankeynode{name=f1, at={[xshift=30mm, yshift=0mm]RFi.north}, anchor=left,
        quantity=\qq{SMBIN}+\Q{vFRONTADV}+\Q{vSHELFFREEZE}+\Q{vML}+\Q{vRFZ},
        forked={\Q{vRFZ}/RFZi, \qq{SMBIN}/SMBINi, \Q{vSHELFFREEZE}/SHELFFREEZEi,
          \Q{vML}/MLi, \Q{vFRONTADV}/FG}}
    } { % mass gain edge case
      \sankeynode{name=f1, at={[xshift=30mm, yshift=0mm]RFi.north}, anchor=left,
        quantity=\qq{SMBIN}+\Q{vFRONTADV}+\Q{vSHELFFREEZE}+\Q{vRFZ},
        forked={\Q{vRFZ}/RFZi, \qq{SMBIN}/SMBINi, \Q{vSHELFFREEZE}/SHELFFREEZEi, \Q{vFRONTADV}/FG}}
    }

@@

    \ifthenelse{\Q{vML} > \Q{vMG}} { % mass loss
      \sankeyfork{f1}{\Q{vRFZ}/RFZo, \Q{vSU}/SU, \Q{vRU}+\Q{vEV}/RUEV,
        \Q{vCALV}/CALV, \Q{vFRONTMELT}/FRONTMELT, \Q{vSHELFMELT}/SHELFMELT,
        \Q{vFRONTRET}/FRONTRET, \Q{vGZRET}/GZ, \Q{vBMB}/BMB}
    }{ % mass gain edge case (AQ_east)
      \sankeyfork{f1}{\Q{vRFZ}/RFZo, \Q{vSU}/SU, \Q{vRU}+\Q{vEV}/RUEV,
        \Q{vCALV}/CALV, \Q{vFRONTMELT}/FRONTMELT, \Q{vSHELFMELT}/SHELFMELT,
        \Q{vFRONTRET}/FRONTRET, \Q{vGZRET}/GZ, \Q{vBMB}/BMB, \Q{vMG}/MG}
    }
    \sankeyturnleft{RFZo}{1}
    \sankeydubins[minimum radius=5mm,ice-to-water-vert]{RFZo}{RFZi}
    \node[font=\tiny, anchor=east]
           at ([yshift=+1.5mm,xshift=1mm]RFZo.north) {\Lab{vRFZ}: \qq{RFZi}};

    \ifthenelse{\Q{vFRONTMELT} > \Q{vSHELFMELT}} { % Greenland
      %% Discharge splits to FRONTMELT (straight) & CALV (above).
      %% SHELFMELT below FRONTMELT. FRONTRET below SHELFMELT.
      \sankeyadvance{FRONTMELT}{20mm}

      \sankeynode{name=SHELFMELTa,quantity=\qq{SHELFMELT},
        at={[yshift=-\yoff, xshift=10mm]FRONTMELT.right}}
      \sankeynode{name=FRONTRETa, quantity=\qq{FRONTRET},
        at={[yshift=-\yoff]SHELFMELTa.right}}
      \sankeyadvance[ice-to-water]{FRONTMELT}{10mm}

@@

      \sankeyset{water}
      \sankeyadvance{FRONTMELT}{10mm}; \sankeyend{FRONTMELT}
      \labelright{FRONTMELT}{vFRONTMELT}
    } {
      % Antarctica
      %% Discharge splits to SHELFMELT (straight) & CALV (above).
      %% No FRONTMELT. Then FRONTRET
      \sankeyadvance{SHELFMELT}{10mm}
      \sankeynode{name=SHELFMELTa, quantity=\qq{SHELFMELT},
        at={[yshift=0, xshift=20mm]SHELFMELT.right}, anchor=right}

      \ifnum \numexpr\Q{vFRONTRET} > 0
        \sankeynode{name=FRONTRETa, quantity=\qq{FRONTRET},
          at={[yshift=-\yoff]SHELFMELT.right}}
        \sankeynode{name=FRONTRETa, quantity=\qq{FRONTRET},
          at={[yshift=-\yoff]SHELFMELTa.right}, anchor=left}
      \fi
      \sankeynode{name=CALVa, quantity=\qq{CALV},
        at={[yshift=\yoff,xshift=0mm]SHELFMELTa.left}, anchor=right}
    }

@@

    %% \sankeynode{name=FRONTRETa, quantity=\qq{FRONTRET}, at={[yshift=-\yoff]SHELFMELTa.right}}
    \ifthenelse{\Q{vFRONTRET} > 0} {
      \sankeyoutin[out-blue]{FRONTRET}{FRONTRETa};
      \sankeynode{name=GZa, quantity=\qq{GZ}, at={[yshift=-\yoff]FRONTRETa.right}, anchor=left}
      \sankeyadvance[out-blue]{FRONTRETa}{10mm}; 
      \sankeyend[out-blue]{FRONTRETa}; \labelright{FRONTRETa}{vFRONTRET}
    } {
      \sankeynode{name=GZa, quantity=\qq{GZ}, at={[xshift=-10mm,yshift=-\yoff]SHELFMELTa.right}, anchor=left}
    }

@@

    \ifnum \numexpr\Q{vFRONTADV} > 0
      \sankeynode{name=FG0, quantity=\qq{FG}, at={[xshift=-15mm,yshift=-6mm]FG.south}, anchor=right}
      \sankeyadvance{FG0}{1mm} \sankeydubins{FG0}{FG}

      \draw[<-,gray] ([xshift=-2mm]FG0.west) -- ++(-10mm,0)
      node[left,font=\tiny,anchor=east,text=black] {Frontal advance: \qq{FG}};
    \fi

>>>>

    \sankeyset{
      def data/.code args={#1/#2/#3}{% node name/label/values
        \LabSet{#1}{#2}
        \QSet{#1}{#3}
        \typeout{#1: \Q{#1} Gt (\Lab{#1})}
      },
      def data/.list={
        %% INSERT_CSV_HERE
        %% COMPUTED
        {vSMBin/SMB Inputs/\Q{vSF}+\Q{vRF}+\Q{vCD}+\Q{vDP}},
        {vINPUT/Inputs/\Q{vSMBin}+\Q{vSHELFFREEZE}},
        {vSMBout/SMB Outputs/\Q{vSU}+\Q{vRU}+\Q{vEV}},
        {vDYN/Dynamics/\Q{vCALV}+\Q{vFRONTMELT}+\Q{vSHELFMELT}+\Q{vGZRET}+\Q{vBMB}},
        {vOUTPUT/Outputs/\Q{vSMBout}+\Q{vDYN}},
        {vSMB/SMB/\Q{vSMBin}-\Q{vSMBout}},
        {vML/Drawdown; Retreat/\Q{vOUTPUT}-\Q{vINPUT}},
        {vMG/Build-up; Expansion/\Q{vINPUT}-\Q{vOUTPUT}}
      },
    }

@@

    \ifthenelse{\Q{vML} > \Q{vMG}} { % mass loss
      \sankeynode{name=f1, at={[xshift=30mm, yshift=0mm]RFi.north}, anchor=left,
        quantity=\qq{SMBIN}+\Q{vSHELFFREEZE}+\Q{vML}+\Q{vRFZ},
        forked={\Q{vRFZ}/RFZi, \qq{SMBIN}/SMBINi, \Q{vSHELFFREEZE}/SHELFFREEZEi,
          \Q{vML}/MLi}}
    } { % mass gain edge case
      \sankeynode{name=f1, at={[xshift=30mm, yshift=0mm]RFi.north}, anchor=left,
        quantity=\qq{SMBIN}+\Q{vSHELFFREEZE}+\Q{vRFZ},
        forked={\Q{vRFZ}/RFZi, \qq{SMBIN}/SMBINi, \Q{vSHELFFREEZE}/SHELFFREEZEi}}
    }

@@

    \ifthenelse{\Q{vML} > \Q{vMG}} { % mass loss
      \sankeyfork{f1}{\Q{vRFZ}/RFZo, \Q{vSU}/SU, \Q{vRU}+\Q{vEV}/RUEV,
        \Q{vCALV}/CALV, \Q{vFRONTMELT}/FRONTMELT, \Q{vSHELFMELT}/SHELFMELT,
        \Q{vGZRET}/GZ, \Q{vBMB}/BMB}
    }{ % mass gain edge case (AQ_east)
      \sankeyfork{f1}{\Q{vRFZ}/RFZo, \Q{vSU}/SU, \Q{vRU}+\Q{vEV}/RUEV,
        \Q{vCALV}/CALV, \Q{vFRONTMELT}/FRONTMELT, \Q{vSHELFMELT}/SHELFMELT,
        \Q{vGZRET}/GZ, \Q{vBMB}/BMB, \Q{vMG}/MG}
    }
    \sankeyturnleft{RFZo}{1}
    \sankeydubins[minimum radius=5mm,ice-to-water-vert]{RFZo}{RFZi}
    \node[font=\tiny, anchor=east]
           at ([yshift=+1.5mm,xshift=1mm]RFZo.north) {\Lab{vRFZ}: \qq{RFZi}};

    \ifthenelse{\Q{vFRONTMELT} > \Q{vSHELFMELT}} { % Greenland
      %% Discharge splits to FRONTMELT (straight) & CALV (above).
      %% SHELFMELT below FRONTMELT.
      \sankeyadvance{FRONTMELT}{20mm}

      \sankeynode{name=SHELFMELTa,quantity=\qq{SHELFMELT},
        at={[yshift=-\yoff, xshift=10mm]FRONTMELT.right}}
      \sankeyadvance[ice-to-water]{FRONTMELT}{10mm}

@@

      \sankeyset{water}
      \sankeyadvance{FRONTMELT}{10mm}; \sankeyend{FRONTMELT}
      \labelright{FRONTMELT}{vFRONTMELT}
    } {
      % Antarctica
      %% Discharge splits to SHELFMELT (straight) & CALV (above).
      %% No FRONTMELT.
      \sankeyadvance{SHELFMELT}{10mm}
      \sankeynode{name=SHELFMELTa, quantity=\qq{SHELFMELT},
        at={[yshift=0, xshift=20mm]SHELFMELT.right}, anchor=right}
      \sankeynode{name=CALVa, quantity=\qq{CALV},
        at={[yshift=\yoff,xshift=0mm]SHELFMELTa.left}, anchor=right}
    }

@@

    \sankeynode{name=GZa, quantity=\qq{GZ}, at={[xshift=-10mm,yshift=-\yoff]SHELFMELTa.right}, anchor=left}

@@
